\subsection{Reputation Service}
\subsubsection{Functionality and Features}
The reputation service provides storage for and access to feedback and reputation reports, for SmartSociety applications.
\subsubsection{Implementation}
\subsubsection{Interfaces, Endpoints and Resources Exposed}
The API currently describes three resources, applications, feedback, and reputation, which are documented below. These API calls are relative to the service’s endpoint, and this service is hosted at https://smartshare.ecs.soton.ac.uk/rs/.
The following actions are available on the service’s resources:
1. GET application/:app/subject/byURI/:subject uri/ Retrieve a subject’s in- formation by its URI. The subject uri must be percentage encoded.
(a) Response Object
The response object and version object are described in Tables 1a and 1a.
versionInfo
an object specifying the version of information contained about a subject.
subject uri
the subject’s URI
feedback
a list of feedback reports about the subject.
currentReputationReport
the current reputation report for a subject.
reputation reports
a list of reputation reports about a subject.
associatedWithEvents
a list of events a subject is associated with through feedback reports.
hasRole
a list roles the subject has played in feedback re- ports.
Table 1: Response Object
Table 2: VersionInfo Object
(b) SmartSociety Example with Authentication via Peer Manager Request
hasAnchor
the current URI of the subject’s information.
previousVersion
the previous URI of the subject’s information.


2. GET application/:app/subject/:subject/ Retrieve information about the sub- ject with the given ID.
versionInfo an object specifying the version of information contained about a subject.
subject uri
the subject’s URI
feedback
a list of feedback reports about the subject.
currentReputationReport
the current reputation report for a subject.
reputation reports
a list of reputation reports about a subject.
associatedWithEvents
a list of events a subject is associated with through feedback reports.
hasRole
a list roles the subject has played in feedback re- ports.




3. POST application/:app/feedback/ Save a new feedback report. (a) Request Body
The request body is a JSON object and it is described in Table 3a. The feedback object contains a set of categories and values which a subject is rated on.

application uri
 
URI of the Application associated with the feed- back.
event uri
URI of the event associated with the feedback.
sub jects
A list of subjects that a feedback report is about.
authors
A list of authors that authored the feedback re- port.
feedback
An object containing feedback categories and rat- ings about the subject/s.
Table 5: Request Body
Table 6: Subject Object
Table 7: Author Object
subject uri
A subject’s URI.
quantifier uri
 
The quantifier URI, which defines the subject’s role in the event.
author uri
An author’s URI.
quantifier uri
 
The quantifier URI, which defines the author’s role in the event.


GET application/:app/reputation/:reputation/ Retrieve the raw reputation report with the given ID.
(a) Response Object
The response object and version object are described in Tables 3b.
Table 9: Response Object
(b) SmartSociety Example with Authentication via Peer Manager
 
timestamp
The timestamp of the feedback report’s submis- sion.
json
A list of categories and ratings which the sub- ject/s were rated.
sub jects
A list of subject/s that the reputation report is about.
reputation id
The id of the reputation report.
uri
The URI of the reputation report.


GET application/:app/opinionOf/:author/aboutSubject/:subject/ Retrieve the raw reputation report about a subject authored by an author.
(a) Response Object
The response object and version object are described in Tables 1a and 1a.
opinion value
 
A value representing an opinion of the author about a subject.
timestamp
A timestamp taken when the opinion was gener- ated.
uri
URI of the opinion.
sub jects
The subject of which the opinion is about.
authors
The author whose feedback reports pertaining to the subject were used to generate the opinion value.


\subsubsection{Repository}